### 2014-03-01 paper/formal.tex
notational changes, improvements to erasure, etc.

How does one characterize what the \emph{secret inputs} of a program
are?  Like other work,~\tocite{} we show specify and prove
noninterference using \emph{term erasure}.
%
Intuitively, term erasure allows us to show that a an
attacker does not learn any sensitive information from a program
written in a non-interference language, if the program behaves identically to the
same program with all sensitive data ``erased.''
%
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function |erasef l| that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than |l| to a new syntactic construct |bullet|.
%
We can generally characterize what features a language must have
in order for the statement of non-interference to be well-posed:

\begin{definition}[Information-flow control language]
    An information-flow control language |L| is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C -> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
In our case, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.  \label{fig:erasure} }
\end{figure}

@@

Non-interference relies on the definition of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
distinguish two configurations that are |l|-equivalent.
%
Since our erasure function captures the attacker model, we simply define this
equivalence as the syntactic-equivalence of erased configurations.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}
%

@@

Directly, we now show that our IFC language satisfies TSNI under a particular
scheduling policy.
%
Specifically, we consider the language under the round-robin scheduler
|roundrobinf| given in Figure~\ref{fig:scheduler}.

@@

In general TSNI will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha (targetLang nop)| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will clearly not satisfy TSNI.
%
In Section~\toref{} we detail the preceise scheduler for which our
specification language is TSNI.
%
Here, we simply remark that even non-adversairal schedulers are not always safe.

Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLang ML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|, we can write the
following program in the specification language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(when false diverge)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(when true diverge)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, however |ic1| will reduce (in two
steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{}.
} then the |sec| thread's decision to diverge or not is directly leaked to a
public entitiy.

In certain cases, however, a TSNI-safe concurrent scheduling policy such as
|roundrobinf| cannot be considered without imposig a non-trivial burden on the
concrete implementation.
%
(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
target language.)
%
Hence, we consider an alternative non-interference property---called termination insensitive
non-interference---that can also be upheld by sequential languages at the cost
of leaking one bit through (non)-termination.
%
\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

>>>>

How can we characterize what the \emph{secret inputs} of a program
are?  Like other work,~\tocite{} we specify and prove
non-interference using \emph{term erasure}.
%
Intuitively, in this approach we proving that an attacker does not learn
any sensitive information from a program by 
Intuitively, term erasure allows us to show that a an
attacker does not learn any sensitive information from a program if the
program behaves identically to a program with all sensitive data ``erased''.
%
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function |erasef il| that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than |il| to a new syntactic construct |bullet|.
%
We can characterize the types of languages for which one can state
a non-interference claim.

\begin{definition}[Information flow control language]
    An information flow control language |L| is a tuple |(C, .->,
    erasef l)|, where $|C|$ is the type of machine configurations (members
    of which are usually denoted by the meta-variable |c|), |.->| is a
    reduction relation between machine configurations and |erasef l : C -> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  This tuple is sometimes
    augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
In our case, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function |erasef il|.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' tS ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.  \label{fig:erasure} }
\end{figure}

@@

Non-interference relies on the definition of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
distinguish two configurations that are |l|-equivalent.
%
Since our erasure function captures the attacker model, we simply define this
equivalence as the syntactic-equivalence of erased configurations.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase il c'|.
\end{definition}
%

@@

We now show that our IFC language satisfies TSNI under a particular
scheduling policy.
%
Specifically, we consider the language under the round-robin scheduler
|roundrobinf| given in Figure~\ref{fig:scheduler}.

@@

In general TSNI will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will clearly not satisfy TSNI.
%
In Section~\toref{} we detail the preceise scheduler for which our
specification language is TSNI.
%
Here, we simply remark that even non-adversairal schedulers are not always safe.

Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.  We can write the
following program in the specification language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(when false diverge)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(when true diverge)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, however |ic1| will reduce (in two
steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{}.
} then the |sec| tasks's decision to diverge or not is directly leaked to a
public entitiy.

In certain cases, however, a TSNI-safe concurrent scheduling policy such as
|roundrobinf| cannot be considered without imposig a non-trivial burden on the
concrete implementation.
%
(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
target language.)
%
Hence, we consider an alternative non-interference property---called termination insensitive
non-interference---that can also be upheld by sequential languages at the cost
of leaking one bit through (non)-termination.
%
\begin{definition}[Termination insensitive non-interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

### 2014-03-01 paper/retrofit.tex
More small fixes.
notational changes, improvements to erasure, etc.

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta | unit
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fail
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) unit |}

\and
\inferrule[T-fail]
{ }
{| conf tS ( tE [ fail ] ) -> conf tS fail |}
\end{mathpar}

@@

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|),
    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues |iS|, and
    \item a forking operation allowing to spawn new tasks, which will be described in more detail in the next section.
\end{itemize}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | iS [ id mapsto Q ]
\end{code}

@@

\begin{mathpar}
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

@@

\begin{figure}
  Concurrent, round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin D (it1, it2, ldots)     = it2, ldots
  roundrobin N (it1, it2, ldots)     = it2, ldots
  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq N (it1, it2, ldots)        = it1, it2, ldots
  seq D (it)                     = it
  seq D (it1, it2, ldots)        = it2, ldots
  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\label{fig:scheduler}
\end{figure}

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.  These rules only operate on the first task in the task pool, which by convention, is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.  The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.  Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
    \item Finally, we define some rules for scheduling, handling forking tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
\end{itemize}

The \textsc{I-fork} rule is of particular interest, as it is intended to allow users
to create new tasks.  When a new task is created, there is a question of what the
global state of the new task should be; this is defined in terms of a function $\kappa$.
Conservatively, $\kappa$ may be simply thought of as the identity function, in which
case the semantics of fork are such that the state of the target language is \emph{cloned}
when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of $\kappa$.

@@

\begin{align*}
    & |let i = TI (fork (x, i' <= brecv . (IT (!(TI x)))))| \\
    & |in TI (send (IT (ref true)))|
\end{align*}

It would be a violation of information flow if such an operation actually
resulted in references being shared between two tasks.  In fact, the address
will be received by the forked task, but it will be a dangling pointer; the
task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
who are curious whether or not a static discipline could be enforced to
prevent these dangling pointers should check Section~\ref{sec:extensions}.)

\paragraph{Status of the heap after a fork}  Here is a program whose
semantics depends on the definition of $\kappa$:

\begin{align*}
    & |let x = ref true| \\
    & |in TI (fork (IT (!x; !x))); x := false|
\end{align*}

When $\kappa$ is the identity, the forked task successfully dereferences
the contents of the reference to be true twice (recall that references
are cloned into the new global state).  When $\kappa$ is the constant function
to the empty store, $x$ becomes a dangling pionter.

@@

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler}, the behavior of \textbf{fork}
can be used to model the behavior of \textbf{toLabeled}:

\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let pid = taskId; | \\
    & |tab let i = TI (fork (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
\end{align*}

When the sequential scheduler is used, the forked task runs to
completion before returning to the task that forked it.  Thus,
a task pool should rather be interpreted as a number of information-flow
aware stack frames.  To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

\and
\inferrule[T-ass]
{ |(ta, tv) in tS| }
{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}

%\and
%\inferrule[T-fail]
%{ }
%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
\end{mathpar}

@@

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|),
    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues |iS|, and
    \item a sandboxing operation allowing to spawn new
    isolated tasks, which will be described in more detail in the
    next section.
\end{itemize}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  sandbox ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | iS [ id mapsto Q ]
\end{code}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

@@

\begin{figure}
  Concurrent, round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin done (it1, it2, ldots)     = it2, ldots
  roundrobin nostep (it1, it2, ldots)     = it2, ldots
  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq nostep (it1, it2, ldots)        = it1, it2, ldots
  seq done (it)                     = it
  seq done (it1, it2, ldots)        = it2, ldots
  seq box (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\label{fig:scheduler}
\end{figure}

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for $\mathcal{E}_{\tar{\Sigma}}$ and $\mathcal{E}_{\ifc{\Sigma}}$.  These rules only operate on the first task in the task pool, which by convention, is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.  The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy $\alpha$.  Not all schedulers preserve non-interference, so we provide two specific schedules in Figure~\ref{fig:scheduler}.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language) and intermediating between the borders of the two languages.
\end{itemize}

The \textsc{I-sandbox} rule is of particular interest, as it is intended to allow users
to create new tasks.  When a new task is created, there is a question of what the
global state of the new task should be; this is defined in terms of a function $\kappa$.
Conservatively, $\kappa$ may be simply thought of as the identity function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for $\kappa$
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of $\kappa$.

For any target language |targetLang| and scheduling policy |alpha|, this
embedding defines an information flow control language, which we will
refer to as |specLang alpha targetLang|.

@@

\begin{align*}
    & |let i = TI (sandbox (x, i' <= brecv . (IT (!(TI x)))))| \\
    & |in TI (send (IT (ref true)))|
\end{align*}

It would be a violation of information flow if such an operation actually
resulted in references being shared between two tasks.  In fact, the address
will be received by the sandboxed task, but it will be a dangling pointer; the
task will become stuck and removed from execution by \textsc{I-noStep}.  (Readers
who are curious whether or not a static discipline could be enforced to
prevent these dangling pointers should check Section~\ref{sec:extensions}.)

\paragraph{Status of the heap after a sandbox}  Here is a program whose
semantics depends on the definition of $\kappa$:

\begin{align*}
    & |let x = ref true| \\
    & |in TI (sandbox (IT (!x; !x))); x := false|
\end{align*}

When $\kappa$ is the identity, the sandboxed task successfully dereferences
the contents of the reference to be true twice (recall that references
are cloned into the new global state).  When $\kappa$ is the constant function
to the empty store, $x$ becomes a dangling pionter.

@@

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler}, the behavior of |sandbox|
can be used to model the behavior of \textbf{toLabeled}:

\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let pid = taskId; | \\
    & |tab let i = TI (sandbox (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
\end{align*}

When the sequential scheduler is used, the sandboxed task runs to
completion before returning to the task that sandboxed it.  Thus,
a task pool should rather be interpreted as a number of information-flow
aware stack frames.  To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}
